Secure Composition of Robust and Optimising Compilers

### 2023-07-05 popl/main.tex

A {\em compiler} ($\cc{\src{L}}{\trg{L}}$) translates syntactic descriptions of programs from a {\em source} ($\src{L}$) into a {\em target} ($\trg{L}$) programming language.
For the syntactic description of programs written in $\src{L}$, this paper writes $\src{\progvar}$, while for ones written in $\trg{L}$, this paper writes $\trg{\progvar}$.
It is considered good if this translation is semantics-preserving, i.e., correct.
Correct compilers may still be insecure compilers\MK{citation needed}.
Programs translated by insecure compilers may violate security properties that were assumed to hold, given the presence of a context--level program.
So, ideally, a compiler is secure~\cite{abate2019jour} in the sense of the following definition:

>>>>

A {\em compiler} ($\cc{\src{L}}{\trg{L}}$) translates syntactic descriptions of programs from a {\em source} ($\src{L}$) into a {\em target} ($\trg{L}$) programming language.\MP{good sentence}
For the syntactic description of programs written in $\src{L}$, this paper writes $\src{\progvar}$, while for ones written in $\trg{L}$, this paper writes $\trg{\progvar}$.\MP{not a fan of this sentence}
It is considered good if this translation is semantics-preserving, i.e., correct. \MP{passive}
Correct compilers may still be insecure compilers\MK{citation needed}.
Programs translated by insecure compilers may violate security properties that were assumed to hold, given the presence of a context--level program.
So, ideally, a compiler is secure~\cite{abate2019jour} in the sense of the following definition:
\MPin{does not really flow.
% 
start with compilers (as now),
then: for a compiler to be correct we expect ... ... (no def)
then: for a compiler to be secure we use the robust compilation framework of ... that says ... ... def
}
